Preparing for Potential Closure of European Airspaces due to Re-entering Space Objects

### 2025-03-07 paper.qmd
added plot for density (of aircraft, population) data storage

) |> 
  gt() |> 
   cols_label(
    resolution ~ "Resolution",
    tidyselect::ends_with("area") ~ "Density, {{*persons* km^-2}}",
    # hex_area ~ md("Cell Area ({km^2}})"),
    hex_edge ~ "Edge length ({km}})"
  ) |> 
    gt::tab_header(
    title = md("H3 Cell Statistics"),
    subtitle = md("average hexagons")
  ) |> 
  opt_align_table_header(align = "left")
```

@@

>>>>

) |> 
  gt() |> 
   cols_label(
    resolution ~ "Resolution",
    tidyselect::ends_with("area") ~ "Cell Area {{*persons* km^-2}}",
    # hex_area ~ md("Cell Area ({km^2}})"),
    hex_edge ~ "Edge length ({km}})"
  ) |> 
    gt::tab_header(
    title = md("H3 Cell Statistics"),
    subtitle = md("average hexagons")
  ) |> 
  opt_align_table_header(align = "left")
```

@@

# Data

::: {#fig-data-densities}

```{r densities}
#| out-width: "120%"
#| echo: false
knitr::include_graphics("media/figures/cubes.pdf")
```

Flight and population densities data (hex on Germany as an example).
:::
